Manuscript Figures

### 2021-06-01 src/manuscript_figures.Rmd
drop one-vs-all pancancer subtype prediction benchmark

# predictability of subtypes using pancancer LFs
pancancer_subtype_stats <- predict_labels(LFs, surv, tcga_subtypes, 'pancancer', 
                                  'cnv_gex_meth_mut', label.type = 'subtype', num.trees = 1000)

p1 <- plot_comp1(pancancer_subtype_stats) + theme(axis.title.x = element_blank())
p2 <- plot_comp2(pancancer_subtype_stats)
# plot subtype specific factors
M <- LFs$maui_factors$pancancer.cnv_gex_meth_mut
st <- tcga_subtypes[match(rownames(M), bcr_patient_barcode)]$Subtype_Selected
# remove NA values and pick subtypes with at least 20 samples 
selected <- names(which(table(st) > 20))
M <- M[st %in% selected,]
labels <- tcga_subtypes[match(rownames(M), bcr_patient_barcode)]$Subtype_Selected

p3 <- plot_label_specific_vars(M, labels)

# data type contribution to top LF per factor
p4 <- plot_datatype_contribution_by_factor(LFs, FWs, 'maui_factors', 
                                           'pancancer', 'cnv_gex_meth_mut', factors = st, 
                                           top_lfs = 1, top_features = 100) 
p4 <- p4 + labs(y = 'Relative Contribution\nto top latent factor') + 
  theme(legend.position = 'right', legend.background = element_blank())

Fig <- plot_grid(plot_grid(plot_grid(p1, p2 + theme(axis.text.x = element_text(angle = 45)), 
                                     nrow = 2, labels = c('A', 'B')), 
                           p3 + theme(legend.position = 'none', 
                                      axis.text.x = element_text(angle = 45)), 
                           labels = c('', 'C'), ncol = 2, rel_widths = c(1,3)), 
                 p4 + theme(axis.text.x = element_text(angle = 45)), 
                 labels = c('', '', 'D'), ncol = 2, rel_widths = c(2.5,1))

supFig_count <- supFig_count + 1
SuppFigures[[supFig_count]] <- Fig
fig.name <- paste0('SuppFigure', supFig_count, '.pancancer_subtype_prediction.pdf')
names(SuppFigures)[supFig_count] <- fig.name
ggsave(file.path(FigureFolder, fig.name), 
              plot = Fig, units = 'in', width = 18, height = 12)
SuppLegends[[supFig_count]] <- "Predictive power of latent factors in distinguishing known TCGA cancer subtypes A-B) comparing MAUI with PCA/MOFA/MCIA. AUC: Area under the ROC curve computed on the test dataset (30% of held-out data) trained on 70% of the dataset using a Random Forest model. Each point represents one cancer subtype (pairwise one-sided Wilcoxon test on AUCs, alternative = maui AUC is not greater than others) C) Top maui LFs detected per cancer subtype (only displaying subtypes with at least 20 samples). Size/color/opacity of the points represent the average neural activation value of the LF for the corresponding subtype samples. D) Percentage of top feature types contributing to top predictive maui latent factor per cancer subtype."
```

>>>>

```
